\TheTitle

### 2017-07-13 paper/study.tex
Correctness results for summarization tasks

The purpose of the study is to quantitatively and qualitatively evaluate
the effectiveness of \tool compared to the DAG-based visualizations
found in Gitk or the git command line. The study is broken into three
task-based sections; conceptual tasks, summarization tasks, and
participant opinions. The study was performed in June of 2017 in
Kingston ON, in a controlled environment running Ubuntu 14.04.
Participants were allowed to use both Gitk and the git command line
tools together, which we will refer to as the git tools. Then they were
asked to perform the same tasks using \tool.

@@

In Figure~\ref{fig:summarization_results}, we see all of the
correctness, accuracy, and timing results. The first row of plots are
the correctness results. \dmg{be more direct: we see that linvis outperforms gitk by a large margin (then you can
  clarify with the statement you have below; otherwise you are asking the reader to make that connection; don't leave
  that to chance. be explicit on what the results tell you, at the high level.)}
We see in all cases except for T10, that the
number of instances of a correct result with \tool is roughly the same
as the number of incorrect instances with Gitk.
\dmg{you don't test the task. You test what? the statistical significance than one tool is better than the other? Again,
  be explicit}
We test each task with
the McNemar Chi-square test~\cite{McNemar1947}.\dmg{don't break the paragraphs here.. you keep talking about the
  test. If you need to break them, break them before this sentence, not after}

@@

\dmg{McNemar is used to test if there was an effect on the tool used in the correctness of the answers of the
  users. It is not an analysis of the participants. Don't elaborate on what it does or does not. Just leave it at what
  it does: if you want to be precise you can say it ``marginal homogeneity'' of the answers}

With the McNemar's tests, we analyze the participants that change from
being correct with one tool to being incorrect with the other. \dmg{Again, never, ever, use a pronom like this to start
  a stence. State that this is instead: The McNemar test..., but i vote for removing this info} This does
not take into account the number of people who were able to provide the
correct answer for both tools, nor the people who were incorrect for both
tools. \dmg{this is better, see my comment before this paragraph, you can use this sentence instead, except: not the
  results: the test is used to test the hypothesis that ...} The results show whether providing the participants with \tool
over the current standard, gitk, improves the correctness of the
summarization tasks among the participants. \dmg{Change it to Table shows..., we don't show, we wrote} We show the results for the
number of people who were, with both tools, correct, incorrect, and
changed in Table~\ref{tab:correctness_table}.

In all cases, except for task T10, \dmg{we don't ``see'', ``these is'' instead: in all cases.. there the differences
  are statistically significant} we saw statistically significant
results \dmg{remove suggesting} suggesting that we reject the null hypothesis \dmg{did you tell us what the null hypo
  is?}. \dmg{say this before making conclusions about the results} We tested each
correctness with an $\alpha = 0.005$. The $\chi^2$ test value with one
degree of freedom is $7.879$.\dmg{what is this number? what is it used for? where does it come from?}

\begin{table*}[htpb]
  \centering
  \caption{Correctness tables showing how many people stayed correct,
    incorrect, and how many people changed between tool}
  \label{tab:correctness_table}
  \begin{tabular}{c|c|c}

    T4 & T5 & T6\\
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular} &

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
      & Incorrect & 14                           & 4\\
    \end{tabular}

    &

@@

    \\\hline
    T7 & T8 & T9\\

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 8                            & 0\\
      & Incorrect & 13                           & 2\\
    \end{tabular}  &
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular} &
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
      & Incorrect & 14                           & 3\\
    \end{tabular}\\\hline

    & T10 & \\
    & \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
      & Incorrect & 8                            & 0\\
    \end{tabular} & \\

  \end{tabular}
\end{table*}

The correctness test statistics and conclusion for each summarization
task;

The correctness test statistics, conclusions, and a description of the
accuracy and timing results for each summarization task follow:

\begin{itemize}

@@

    T4; the resulting $\chi^2$ value is $15$. $15 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining the series of merges that a commit
    takes, with $99.5\%$ confidence.

    There is almost no variation in accuracy between participants using
    \tool, while there is more variance in Gitk. There were two outliers
    among the instances using \tool, which lie within the second and
    third quartiles for the accuracy measure of Gitk. The furthest
    outlier for \tool lies at a distance that is slightly greater than
    the median for Gitk.

    We see similar results in the timing metric; all significant data
    occurs within less time than the second, third, and fourth quartile
    of the Gitk results. Nearly all outlier instances in \tool are
    within the third quartile group of the instances of Gitk with the
    exception of the most extreme, which lies in the fourth quartile
    group.

    The results indicate that \tool is able to assist users with
    determining how a commit is merged more accurately, and more
    quickly.

@@

    T5; the resulting $\chi^2$ value is $14$. $14 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining the other related commits, with
    $99.5\%$ confidence.

    There is very little variance in the accuracy of results for \tool
    compared to the accuracy of the results in Gitk. The median distance
    is smaller, indicating that the participants performed more
    accurately using \tool.

    There is less variance in the time taken to come to an answer with
    \tool than with Gitk. Furthermore, we see that a majority of the
    participants were able to complete the task in \tool in much less
    time than 50\% of the participants using Gitk.

    The results indicate that \tool is able to assist users in
    understanding which commits are related to a given commit.

@@

    T6; the resulting $\chi^2$ value is $16$. $16 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining the number of authors involved with
    the merge tree, with $99.5\%$ confidence.

    We see the same results from this task as with the previous tasks,
    suggesting that \tool assists users determine the number of authors
    more quickly and more accurately.

@@

    T7; the resulting $\chi^2$ value is $13$. $13 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining who contributed the most changes,
    with $99.5\%$ confidence.

    This question does not include an accuracy metric, as there are only
    two possible outcomes. We see the same result in the timing metric
    as we did from the previous questions.

    The results suggest that \tool is able to help users correctly
    identify the person who contributed the most lines of code to a
    merge tree in less time.

    T8; the resulting $\chi^2$ value is $15$. $15 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining how many files were contributed,
    with $99.5\%$ confidence.

    The results of this task are the same as in the previous tasks.
    This suggest that \tool is able to assist users determine how many
    files were modified, more quickly and more accurately.

    T9; the resulting $\chi^2$ value is $14$. $14 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining which file had the most changes,
    with $99.5\%$ confidence.

    While this question appears to have a similar answer to the correct
    answer for T7, the answer \comA had two files with the same number
    of midifications, thus the participant must correctly identify both
    of these files to be correct. For this reason, we include an
    accuracy metric.

    The results of this task are the same as the previous tasks.
    This suggests that \tool is able to assist users to determine which
    file had the most changes.

    T10; the resulting $\chi^2$ value is $5.44$. $5.44 < 7.879$,
    therefore we do not reject the null hypothesis, suggesting that
    \tool does not make a difference in determining which modules are
    involved with a merge tree.

    The accuracy and timing results for this task are the same as the
    others, showing that there is less variability in both accuracy and
    the time taken to have an answer between participants using \tool
    than using Gitk. Looking Table~\ref{tab:correctness_table}, we can
    see that, unlike the other questions, a majority of the participants
    were correct using both tools.

>>>>

The purpose of the study is to quantitatively and qualitatively evaluate
the effectiveness of \tool compared to the DAG-based visualizations
found in Gitk or the git command line. The study is broken into three
task-based sections; conceptual tasks, summarization tasks, and
participant opinions. The study was performed in June of 2017 in
Kingston ON, in a controlled environment running Ubuntu 14.04.
Participants were allowed to use both Gitk and the git command line
tools together, which we will refer to as the git tools or as Gitk. Then
they were asked to perform the same tasks using \tool.

@@

% TODO: Add the null hypotheses for each question to the procedures
% TODO: Include the Wilcoxon Test and Cliff effect size test results

The results show ( Figure~\ref{fig:summarization_results} ) that in all
cases, except for T10, the number of instances of a correct result with
\tool is roughly the same as the number of incorrect instances with
gitk. \tool outperforms Gitk in correctness by a large margin. We use
the McNemar Chi-square test~\cite{McNemar1947} with continuity
correction to test the statistical significance of the hypothesis that
\tool improves the correctness of the participants. We use $\alpha =
0.05$, or a $95\%$ confidence level, therefore the $\chi^2$ test
statistic is 3.841.

@@

\begin{table}[htpb]
  \centering
  \caption{Correctness Results}
  \label{tab:correctness_table}
  \begin{tabular}{crrc}
    \toprule
    Task & $\chi^2$ & $p$-value & Conclusion\\\midrule
    T4   & 13.07    & 0.0003    & Reject $H_0$\\
    T5   & 12.07    & 0.0005    & Reject $H_0$\\
    T6   & 14.06    & 0.0002    & Reject $H_0$\\
    T7   & 11.07    & 0.0009    & Reject $H_0$\\
    T8   & 13.07    & 0.0003    & Reject $H_0$\\
    T9   & 12.07    & 0.0005    & Reject $H_0$\\
    T10  & 4.00     & 0.0455    & Reject $H_0$\\
    \bottomrule
  \end{tabular}
\end{table}

The results for the correctness metric are summarized in
Table~\ref{tab:correctness_table}; the full results are as follows;

% TODO: add results for other metrics

\begin{itemize}
  \item

    T4; The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
                            & Incorrect & 15                           & 2\\
    \end{tabular}\\

    T5; The $\chi^2$ statistic is $12.07$ with a p-value of $0.0005$.
    $12.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 5                            & 0\\
                            & Incorrect & 14                           & 4\\
    \end{tabular}\\

    T6; The $\chi^2$ statistic is $14.06$ with a p-value of $0.0002$.
    $14.06 > 3.841$ and $0.0002 < 0.05$, therefore we reject the null
    hypothesis.

@@

@@

    T7; The $\chi^2$ statistic is $11.07$ with a p-value of $0.0009$.
    $11.07 > 3.841$ and $0.0009 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 8                            & 0\\
                            & Incorrect & 13                           & 2\\
    \end{tabular}\\

@@

    T8; The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
                            & Incorrect & 15                           & 2\\
    \end{tabular}\\

@@

    T9; The $\chi^2$ statistic is $12.07$ with a p-value of $0.0005$.
    $12.07 > 3.841$ and $0.0005 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
      & Incorrect & 14                           & 3\\
    \end{tabular}

@@

    T10; The $\chi^2$ statistic is $4$ with a p-value of $0.0455$.
    $4 > 3.841$ and $0.0455 < 0.05$, therefore we reject the null
    hypothesis. The p-value is very close to the $\alpha$ value in this
    case, so the conclusion is not as well defined.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
      & Incorrect & 8                            & 0\\
    \end{tabular}
